Cognitive Principles and Individual Differences \\ in Human Syllogistic Reasoning

### 2019-11-14 paper/paper-v3.tex
added Luka nec operator ref

We consider the three-valued {\L}ukasiewicz logic~\cite{lukasiewicz:20}
extended with the $\cxt$ connective, for which the
corresponding truth values are $\top$, $\bot$ and $\udf$, meaning \textit{true}, \textit{false}
and \textit{unknown}, respectively.
% As it seems,  $\cxt$ corresponds to {\L}ukasiewicz necessity operator~\cite{}, where the difference is, that $\cxt$ is restricted to be applicable to literals only.
A \defname{three-valued interpretation}~$I$ is a mapping from the set of
logical formulas to the set
of truth values~$\{ \true, \bot, \udf\}$, represented as a pair~$I~=~\langle I^\true,I^\bot \rangle$ of two disjoint sets of atoms:  $I^\true =  \{A \mid A \mbox{ is mapped to } \true \mbox{ under } I\}$ and $I^\bot = \{A \mid A \mbox{ is mapped to } \bot \mbox{ under } I \}$.
Atoms which do not occur in~$I^\true \cup I^\bot$ are mapped to~$\udf$.
The truth value of a given formula
under $I$ is determined according to the truth tables in
Table~\ref{tab:3vldluka}.
$I(F) = \top$ denotes that a formula $F$ is mapped to true under $I$.
A \defname{three-valued model} $\CalM$ of~$\CalP$ is a three-valued interpretation such that
$\CalM(A \leftarrow \Body) = \true$ for each $A \leftarrow \Body \in \Ground\CalP$.
Let $I = \langle I^\top, I^\bot \rangle$ and $J = \langle J^\top,
J^\bot \rangle$ be two interpretations.
$I \subseteq J$ iff $I^\top \subseteq J^\top$ and $I^\bot \subseteq J^\bot$. $I$ is the \textit{least model} of $\CalP$
iff for any other model~$J$ of $\CalP$ it holds that $I \subseteq J$.

@@

Another interesting aspect is to investigate in how far the semantics of the $\cxt$ operator within the extended three-valued {\L}ukasiewicz logic in Section~\ref{sub:3valuedL} 
 corresponds to the {\L}ukasiewicz extensional necessity operator~\cite{}\todo{R: Referenz fehlt}.\footnote{Thanks to the
 anonymous reviewer for this observation.}

>>>>

We consider the three-valued {\L}ukasiewicz logic~\cite{lukasiewicz:20}
extended with the $\cxt$ connective, for which the
corresponding truth values are $\top$, $\bot$ and $\udf$, meaning \textit{true}, \textit{false}
and \textit{unknown}, respectively.
% As it seems,  $\cxt$ corresponds to {\L}ukasiewicz necessity operator~\cite{}, where the difference is, that $\cxt$ is restricted to be applicable to literals only.
A \defname{three-valued interpretation}~$I$ is a mapping from the set of
logical formulas to the set
of truth values~$\{ \true, \bot, \udf\}$, represented as a pair~$I~=~\langle I^\true,I^\bot \rangle$ of two disjoint sets of atoms:  $I^\true =  \{A \mid A \mbox{ is mapped to } \true \mbox{ under } I\}$ and $I^\bot = \{A \mid A \mbox{ is mapped to } \bot \mbox{ under } I \}$.
Atoms which do not occur in~$I^\true \cup I^\bot$ are mapped to~$\udf$.
The truth value of a given formula
under $I$ is determined according to the truth tables in
Table~\ref{tab:3vldluka}.
\footnote{Thanks to the
 anonymous reviewer for the observation, that the $\cxt$ operator seems to be a special case of {\L}ukasiwicz's necessity operator~\cite[p. 20]{malinowski:1993}, restricted to literals.
 }

$I(F) = \top$ denotes that a formula $F$ is mapped to true under $I$.
A \defname{three-valued model} $\CalM$ of~$\CalP$ is a three-valued interpretation such that
$\CalM(A \leftarrow \Body) = \true$ for each $A \leftarrow \Body \in \Ground\CalP$.
Let $I = \langle I^\top, I^\bot \rangle$ and $J = \langle J^\top,
J^\bot \rangle$ be two interpretations.
$I \subseteq J$ iff $I^\top \subseteq J^\top$ and $I^\bot \subseteq J^\bot$. $I$ is the \textit{least model} of $\CalP$
iff for any other model~$J$ of $\CalP$ it holds that $I \subseteq J$.

@@
